Popularity Adjusted Block Models are Generalized Random Dot Product Graphs

### 2022-03-29 fls-lightning-talk/slides.Rmd
numbered items on slide 4 are one line each now
figured out how to add images to title slide

---
title: Popularity Adjusted Block Models are Generalized Random Dot Product Graphs
subtitle: Future Leaders Summit 2022 Lightning Presentation
author: John Koo, Indiana University
date: 'April 2022'
output: 
  beamer_presentation:
    fig_crop: no
    theme: 'default'
    colortheme: 'beaver'
    includes:
      in_header: page_headers.tex
header-includes:
- \usepackage{setspace}
- \usepackage{float}
- \usepackage{mathtools}
- \usepackage{natbib}
- \usepackage[linesnumbered,ruled,vlined]{algorithm2e} 
- \setcitestyle{numbers,square,comma}
- \usepackage{verbatim}
- \usepackage{amsthm}
- \usepackage{comment}
- \usepackage{graphicx}
- \setbeamertemplate{itemize items}[circle]
---

@@

## Contributors

@@

```{r, out.width = '100px'}
knitr::include_graphics('john-koo.jpeg')
```

@@

```{r, out.width = '100px'}
knitr::include_graphics('minh-tang.jpg')
```

@@

```{r, out.width = '100px'}
knitr::include_graphics('michael-trosset.jpg')
```

@@

1. $P$ is an $n \times n$ matrix of edge probabilities between pairs of vertices.
2. $A_{ij} \indep \Bernoulli(P_{ij})$ for each $i < j$.

@@

```{r, fig.height = 3, fig.width = 4, out.width = '100%', fig.cap = 'Two community SBM with $p=1/2$, $q=1/4$, $r=1/8$'}
n1 <- 2 ** 5
n2 <- 2 ** 5
n <- n1 + n2
z <- c(rep(1, n1), rep(2, n2))
p <- 1/2
q <- 1/4
r <- 1/8
P <- matrix(r, nrow = n, ncol = n)
P[seq(n1), seq(n1)] <- p
P[seq(n1 + 1, n), seq(n1 + 1, n)] <- q
A <- draw.graph(P)
qgraph::qgraph(A, vsize = 4, groups = factor(z), legend = FALSE)
```

@@

We compared a variety of algorithms for community detection on randomly generated PABMs:

* Modularity Maximization (Sengupta and Chen) using the Louvain algorithm;
* Orthogonal Spectral Clustering (KTT);
* Sparse Subspace Clustering on the ASE (KTT);
* Sparse Subspace Clustering on the columns of $A$ (Noorozi, Rimal, Pensky).

@@

@@

>>>>

---
output: 
  beamer_presentation:
    keep_tex: true
    fig_crop: no
    theme: 'default'
    colortheme: 'beaver'
    includes:
      in_header: 
        - page_headers.tex
header-includes:
- \usepackage{setspace}
- \usepackage{float}
- \usepackage{mathtools}
- \usepackage{natbib}
- \usepackage[linesnumbered,ruled,vlined]{algorithm2e} 
- \setcitestyle{numbers,square,comma}
- \usepackage{verbatim}
- \usepackage{amsthm}
- \usepackage{comment}
- \usepackage{graphicx}
- \setbeamertemplate{itemize items}[circle]
---

@@

## {.plain}

\center

\LARGE

\textcolor{darkred}{Popularity Adjusted Block Models are Generalized Random Dot Product Graphs}

\normalsize

Future Leaders Summit

April 2022

@@

```{r, out.width = '75px'}
knitr::include_graphics('john-koo.jpeg')
```

@@

```{r, out.width = '75px'}
knitr::include_graphics('minh-tang.jpg')
```

@@

```{r, out.width = '75px'}
knitr::include_graphics('michael-trosset.jpg')
```

@@

1. $P$ is a matrix of edge probabilities between pairs of vertices.
2. $A_{ij} \indep \Bernoulli(P_{ij})$ for each $i < j$.

@@

```{r, fig.height = 3, fig.width = 4, out.width = '100%', fig.cap = 'SBM with $p=1/2$, $q=1/4$, $r=1/8$'}
n1 <- 2 ** 5
n2 <- 2 ** 5
n <- n1 + n2
z <- c(rep(1, n1), rep(2, n2))
p <- 1/2
q <- 1/4
r <- 1/8
P <- matrix(r, nrow = n, ncol = n)
P[seq(n1), seq(n1)] <- p
P[seq(n1 + 1, n), seq(n1 + 1, n)] <- q
A <- draw.graph(P)
qgraph::qgraph(A, vsize = 4, groups = factor(z), legend = FALSE)
```

@@

We compare four algorithms for community detection on randomly generated PABMs:

* Modularity Maximization (Sengupta and Chen) using the Louvain algorithm;
* Orthogonal Spectral Clustering (KTT);
* Sparse Subspace Clustering on the columns of $A$ (Noorozi, Rimal, Pensky); 
* Sparse Subspace Clustering on the ASE (KTT).

@@

## Additional Slides

@@

## Future Work
